Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-18 paper/paper.tex
pass

Table~\ref{table:rules} shows a sample of non-documentation options \rui{what is the meaning of non-documentation in this context?} of
Suricata. Column ``\#'' shows the option number, column ``Name'' shows
the name of the option, and column ``Description'' summarizes
purpose. The option \CodeIn{content} deserves attention. It is common
in rules to capture http attacks and http rules are the most common in
the Emerging Threats Open Ruleset~\cite{emerging-threats-open}. The
content option takes a sequence of bytes as argument and checks if
that sequence is in the payload of the message.  For example, the
option \CodeIn{content:''SELECT''} checks if the string ``SELECT'' is
present in the payload.  Detailed description of the Suricata rules
can be found elsewhere~\cite{suri-rule-format}. Suricata supports a
total of \totoptions\ distinct options covering \numproto\ distinct
network protocols.

>>>>

Table~\ref{table:rules} shows a sample of non-documentation options \rui{what 
is the meaning of non-documentation in this context?} \Luc{documentation options
are options that gives information about the rule itself and are not used for 
matching on packet data. So, non-documentation options are the ones that really
matters for detection.} of Suricata. Column ``\#'' shows the option number, column 
``Name'' shows the name of the option, and column ``Description'' summarizes
purpose. The option \CodeIn{content} deserves attention. It is common
in rules to capture http attacks and http rules are the most common in
the Emerging Threats Open Ruleset~\cite{emerging-threats-open}. The
content option takes a sequence of bytes as argument and checks if
that sequence is in the payload of the message.  For example, the
option \CodeIn{content:''SELECT''} checks if the string ``SELECT'' is
present in the payload.  Detailed description of the Suricata rules
can be found elsewhere~\cite{suri-rule-format}. Suricata supports a
total of \totoptions\ distinct options covering \numproto\ distinct
network protocols.
